---
title: "Finding_Correlation"
output: html_document
date: "2024-09-27"
---
# Finding Correaltion between two attributes for Healthcare

```{r}
df <- read.csv("C:\\Users\\chana\\OneDrive\\Desktop\\USDA_Clean.csv")
```

```{r}
head(df,5)
```
## Checking the datatypes of the attriutes
```{r}
sapply(df, class)
```
## Visualizing correlation among Calories, Protein, Total Fat. Carbohydrate, Sodium and Cholestrole without Normalizing

```{r}
correlation <- cor(df[,
c('Calories','Protein','TotalFat','Carbohydrate','Sodium','Cholesterol')])
View(correlation)
```

## Applying Normalization
```{r}
a= matrix(0,nrow = 6,ncol = 6)
a= as.data.frame(a)
```

```{r}
temp <- 
  c("Calories","Protein","TotalFat","Carbohydrate","Sodium","Cholesterol")
```

```{r}
temp_df <- df[,4:9]
View(temp_df)
```

```{r}
colnames(a) = temp
rownames(a) = colnames(a)
View(a)
```

```{r}
for (i in 1:6)
  for (j in 1:6)
    a[i,j] = cor(temp_df[,i],temp_df[,j])
View(a)
```

```{r}
a = (a-min(a))/(max(a)-min(a))
View(a)
```

### Before normalizing the data the correaltion between Calories and TotalFat was 0.8501546
### After normalization the correlation between Calories and TotalFat is significant because they both have the correlation of 0.804495022

## Creating Linear Regression Model, using Calories as the dependent variable Protein, TotalFat, Carbohydrate, Sodium and Cholrsterol as the independant variables.
```{r}
model <- lm(df$Calories ~ df$Protein + df$TotalFat + df$Carbohydrate + df$Sodium + df$Cholesterol, data=df)
model
summary(model)
```
### After watching the summary we can say that the least significant variable is sodium        because the p-value of sodium is >0.1

## Now lets say a new product is just produced with the following data:                       Protein = 0.1, TotalFat = 35, Carbohydrate = 405, Sodium = 440, Cholesterol = 70, Sugar=    NA, Calcium = 35, Iron = NA, Potassium = 35, VitaminC = 10, VitaminE = NA.                 Based on the model we created we will predict value for Calories.

```{r}
uservalue = matrix(0,nrow = 1,ncol = 5)
uservalue = as.data.frame(uservalue)
colnames(uservalue) <- 
  c("Protein","TotalFat","Carbohydrate","Sodium","Cholesterol")
uservalue[1,1] = 0.1
uservalue[1,2] = 35
uservalue[1,3] = 405
uservalue[1,4] = 440
uservalue[1,5] = 70
```

```{r}
predicted_value <- predict(model,uservalue)
predicted_value
```
### Now lets say sodium amount increases from 440 to 44440, we will see how much change will occur on Calories in percent?
```{r}
uservalue_1 = matrix(0,nrow = 1,ncol = 5)
uservalue_1 = as.data.frame(uservalue_1)
colnames(uservalue_1) <- 
  c("Protein","TotalFat","Carbohydrate","Sodium","Cholesterol")
uservalue[1,1] = 0.1
uservalue[1,2] = 35
uservalue[1,3] = 405
uservalue[1,4] = 44440
uservalue[1,5] = 70
```

```{r}
predicted_value <- predict(model,uservalue_1)
predicted_value
```
```{r}
## When we increased the sodium amount from 444 to 4440 it increases the amount of calories by 0.01%. The reason behind this change is that both are correlated to each other.
```

